---
title: "HUMAN PERCEPTION OF EXPONENTIALLY INCREASING DATA DISPLAYED ON A LOG SCALE EVALUATED THROUGH EXPERIMENTAL GRAPHICS TASKS"
subtitle: "Ph.D. Final Examination"
author: "Emily Robinson"
date: "Department of Statistics, University of Nebraska - Lincoln"
output:
  xaringan::moon_reader:
    seal: false
    includes:
      after_body:
        "js-addins.html"
    mathjax: "https://cdn.bootcss.com/mathjax/2.7.1/MathJax.js?config=TeX-MML-AM_HTMLorMML"
    css: ["default", "metropolis-fonts", "metropolis" ,"css/modal.css", "css/sizeformat.css"]
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightlines: true
      countIncrementalSlides: true
---
class:title-slide-custom

```{r, child = "style.Rmd"}
```


```{r setup, echo = FALSE, message = FALSE, warning = FALSE}
# Packages
library(emoji)
library(purrr)
library(tidyverse)
library(gridExtra)
library(nullabor)
library(scales)
library(knitr)
library(kableExtra)
library(RefManageR)
library(iconr)
library(fontawesome)
# download_fontawesome()

# References
bib <- ReadBib("bib/references.bib", check = FALSE)
ui <- "- "

# R markdown options
knitr::opts_chunk$set(echo = FALSE, 
                      message = FALSE, 
                      warning = FALSE, 
                      cache = FALSE,
                      dpi = 300)
options(htmltools.dir.version = FALSE)
options(knitr.kable.NA = '')
```

```{r, include = F, eval = T, cache = F}
clean_file_name <- function(x) {
  basename(x) %>% str_remove("\\..*?$") %>% str_remove_all("[^[A-z0-9_]]")
}
img_modal <- function(src, alt = "", id = clean_file_name(src), other = "") {
  
  other_arg <- paste0("'", as.character(other), "'") %>%
    paste(names(other), ., sep = "=") %>%
    paste(collapse = " ")
  
  js <- glue::glue("<script>
        /* Get the modal*/
          var modal{id} = document.getElementById('modal{id}');
        /* Get the image and insert it inside the modal - use its 'alt' text as a caption*/
          var img{id} = document.getElementById('img{id}');
          var modalImg{id} = document.getElementById('imgmodal{id}');
          var captionText{id} = document.getElementById('caption{id}');
          img{id}.onclick = function(){{
            modal{id}.style.display = 'block';
            modalImg{id}.src = this.src;
            captionText{id}.innerHTML = this.alt;
          }}
          /* When the user clicks on the modalImg, close it*/
          modalImg{id}.onclick = function() {{
            modal{id}.style.display = 'none';
          }}
</script>")
  
  html <- glue::glue(
     " <!-- Trigger the Modal -->
<img id='img{id}' src='{src}' alt='{alt}' {other_arg}>
<!-- The Modal -->
<div id='modal{id}' class='modal'>
  <!-- Modal Content (The Image) -->
  <img class='modal-content' id='imgmodal{id}'>
  <!-- Modal Caption (Image Text) -->
  <div id='caption{id}' class='modal-caption'></div>
</div>
"
  )
  write(js, file = "js-addins.html", append = T)
  return(html)
}
# Clean the file out at the start of the compilation
write("", file = "js-addins.html")
```

<br><br><br>
## Human Perception of Exponentially Increasing Data Displayed on a Log Scale Evaluated Through Experimental Graphics Tasks
### Ph.D. Final Exmaination
#### Emily A. Robinson
#### Department of Statistics, University of Nebraska - Lincoln
##### `r fa("envelope", fill = "black")` [emily.robinson@huskers.unl.edu](emily.robinson@huskers.unl.edu)
##### `r fa("home", fill = "black")` [www.emilyarobinson.com](https://www.emilyarobinson.com/)
##### `r fa("github", fill = "black")` [earobinson95](https://github.com/earobinson95)
<br><br>
.medium[*Slides: https://bit.ly/3ENZmOZ*]

---
class:primary
# Outline

`r fa_i("chart-line")` Background of graphical testing and measuring patterns

`r fa_i("js")` `r fa_i("plus")` `r fa_i("r-project")` Integration of D3.js and R Shiny

`r fa_i("pen")` Test your drawing skills!

`r fa_i("check")` Validation and Application

`r fa_i("spinner")` Future Work

---
class:primary
# References
<font size="3">
```{r, print_refs1, results='asis', echo=FALSE, warning=FALSE, message=FALSE}
print(bib[[c("finney1951subjective")]], 
      .opts = list(check.entries = FALSE, style = "html", bib.style = "authoryear")
      )
```
</font>

---
class:primary
# Acknowledgements

+ Advisors: Dr. Susan VanderPlas and Dr. Reka Howard

---
class:inverse
<br>
<br>
<br>
.center[
# Thank you! 
<br>
<br>
`r fa("envelope", fill = "white")` **emily.robinson@huskers.unl.edu**
`r fa("home", fill = "white")` **www.emilyarobinson.com**
`r fa("github", fill = "white")` **earobinson95**
]