---
title: "HUMAN PERCEPTION OF EXPONENTIALLY INCREASING DATA DISPLAYED ON A LOG SCALE EVALUATED THROUGH EXPERIMENTAL GRAPHICS TASKS"
subtitle: "Department of Statistics, University of Nebraska - Lincoln"
author: "Emily Anna Robinson"
date: "July 22, 2021"
output:
  xaringan::moon_reader:
    seal: true
    includes:
      after_body:
        "js-addins.html"
    mathjax: "https://cdn.bootcss.com/mathjax/2.7.1/MathJax.js?config=TeX-MML-AM_HTMLorMML"
    # css: ["default", "rladies-fonts", "css/modal.css", "css/this-presentation.css"]
    css: ["default", "metropolis-fonts", "metropolis" ,"css/modal.css", "css/sizeformat.css"]
    # css: [default, metropolis, metropolis-fonts]
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightlines: true
      countIncrementalSlides: true
---

```{r, child = "style.Rmd"}
```


```{r setup, echo = FALSE, message = FALSE, warning = FALSE}

# Packages
library(emo)
library(purrr)
library(tidyverse)
library(gridExtra)
library(nullabor)
library(scales)
library(knitr)
library(kableExtra)
library(RefManageR)
library(iconr)
# download_fontawesome()

# References
bib <- ReadBib("bib/thesis.bib", check = FALSE)
ui <- "- "

# R markdown options
knitr::opts_chunk$set(echo = FALSE, 
                      message = FALSE, 
                      warning = FALSE, 
                      cache = FALSE,
                      dpi = 300)
options(htmltools.dir.version = FALSE)
options(knitr.kable.NA = '')
```

# Outline

1. Background
    + Introduction to Graphics
    + Perception and Psychophysics
    + Testing Graphics
    + Logarithmic Scales and Mapping
    + Underestimation of Exponential Growth
2. Perception of Logarithmic Scales
3. Prediction with You Draw It
4. Eye Fitting Straight Lines in the Modern Era
5. Prediction of Exponential Trends
6. Future Work
7. Conclusion
8. Questions and Discussion

---
class:inverse
.center[
# Background
]

---
class:primary
# Introduction to Graphics

---
class:primary
# Perception and Pyschophysics

---
class:primary
# Logarithmic Perception

---
class:primary
# Graphics Testing

---
class:primary
# Logarithmic Scales and Mapping

---
class:primary
# References


