---
title: "Introduction to R Workshop"
subtitle: "Cal Poly Quantitative Analysis Club"
format: 
  pdf:
    self-contained: true
editor: visual
execute:
  message: false
  warning: false
  error: true
---

[Link to workshop slides](file:///C:/Users/erobin17/Documents/presentations/Seminars/2023.03.02-quantiative-analysis-intro-to-r/intro-to-r.html#/title-slide)

# Introduction to R

R is a programming language designed originally for *statistical analyses.*

# Variable Assignment 

We assign objects in R using the syntax `object_name <- value`

```{r}
message <- "So long and thanks for all the fish"
message
year <- 2025
year

## Add the answer and earth_demolished below

```

# Functions & Function Arguments

+ `vec` -- object name
+ `seq` -- function name
+ `from`, `to`, `by` -- function arguments

```{r}
vec <- seq(from = 1, to = 10, by = 2)
vec
```

```{r}
# Other example base functionality

```

# Packages

```{r}
# install.packages("tidyverse")
library(tidyverse)
```

# Create a graph with me! `ggplot`

Let's load in the data -- learn more about the Palmer Penguins data [here](https://allisonhorst.github.io/palmerpenguins/).

```{r}
library(palmerpenguins)
data(penguins)
head(penguins)
```
Add the `ggplot` layers to the code below:

```{r}
library(ggplot2)
ggplot(data = penguins)

```
# Download R/RStudio

1.  Download and run the R installer for your operating system from CRAN:

    -   Windows: <https://cran.rstudio.com/bin/windows/base/>
    -   Mac: <https://cran.rstudio.com/bin/macosx/> (double check your macOS version)
    -   Linux: <https://cran.rstudio.com/bin/linux/> (pick your distribution)

    If you are on Windows, you should also install the [Rtools4 package](https://cran.rstudio.com/bin/windows/Rtools/); this will ensure you get fewer warnings later when installing packages.

    More detailed instructions for Windows are available [here](https://owi.usgs.gov/R/training-curriculum/installr/)

2.  Download and install the [latest version of RStudio](https://www.rstudio.com/products/rstudio/download/#download) for your operating system.

